### 2022-12-02 writing/manuscript.Rmd
integrating bootstrap code into manuscript

boot_cors <- boot %>% 
  rename_with(~ str_extract(.x, ".*(?=_)"), everything()) %>% 
  map(~ t.test(.x, mu = 0, alternative = "greater"))
```

@@

danc_hist <- boot_plot(danc_cors, color_scheme[1], "<i style='color:#000000;'>\"...for dancing\"</i>", average_boots$danc_cors)
heal_hist <- boot_plot(heal_cors, color_scheme[2], "<i style='color:#000000;'>\"...to heal illness\"</i>", average_boots$heal_cors)
love_hist <- boot_plot(love_cors, color_scheme[3], "<i style='color:#000000;'>\"...to express love for<br>another person\"</i>", average_boots$love_cors)
baby_hist <- boot_plot(baby_cors, color_scheme[4], "<i style='color:#000000;'>\"...to soothe a baby\"</i>", average_boots$baby_cors)

>>>>

boot_cors <- boot %>% 
  map(~ t.test(.x, mu = 0, alternative = "greater"))
```

@@

danc_hist <- boot_plot(boot$danc, color_scheme[1], "<i style='color:#000000;'>\"...for dancing\"</i>", average_boots$danc)
heal_hist <- boot_plot(boot$heal, color_scheme[2], "<i style='color:#000000;'>\"...to heal illness\"</i>", average_boots$heal)
love_hist <- boot_plot(boot$love, color_scheme[3], "<i style='color:#000000;'>\"...to express love for<br>another person\"</i>", average_boots$love)
baby_hist <- boot_plot(boot$baby, color_scheme[4], "<i style='color:#000000;'>\"...to soothe a baby\"</i>", average_boots$baby)
